\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Product Backlog (Requirements Document)}
\date{January 2016}
\author{Matthew Morris \and Terik Brunson \and Justin Hershberger \and Caleb Yearsley \and Corbin Cutler}

\makeatletter
\def\@seccntformat#1{%
  \expandafter\ifx\csname c@#1\endcsname\c@section\else
  \csname the#1\endcsname\quad
  \fi}
\makeatother

\makeatletter
\def\@seccntformat#1{%
  \expandafter\ifx\csname c@#1\endcsname\c@subsection
    \else
  \csname the#1\endcsname\quad
  \fi}
\makeatother

\begin{document}

\maketitle

\section{Problem Statement}
Insert Problem Statement from Project Charter here.

\section{Background Information}

\section{Requirements}

\subsection{Functional Requirements}
\begin{enumerate}
    \item As a user, I would like to be able to create an account.
    \item As a user, I would like to be able to log in and out of my account.
    \item As a user, I would like to be able to change my account information.
    \item As a user, I would like to be able to add others' accounts as friends.
    \item As a user, I would like to be able to view my list of friends.
    \item As a user, I would like to be able to view my profile page, and friends' profile pages.
    \item As a user, I would like to be able to post movie reviews and my rating of that movie.
    \item As a user, I would like to be able to make a list of movies that I can post.
    \item As a user, I would like to be able to comment on others' movie reviews and rating.
    \item As a user, I would like to be able to 'like' a post made by a user.
    \item As a user, I would like to be able to view highest rated movies among critics, friends, and other website users.
    \item As a user, I would like to be able to view lowest rated movies among critics, friends, and other website users.
    \item As a user, I would like to be able to search for a movie and view information about that movie, such as genre, actors, director, writers, producers, links to trailers, award nominations, and awards.
    \item As a user, I would like to be able to see what movies are popular right now.
    \item As a user, I would like to be able to 
\end{enumerate}

\subsection{Non-Functional Requirements}
\begin{enumerate}
    \item Use IMDB's API.
    \item Create and store information in our PostgreSQL database.
    \item Program in Python, Javascript, and Boostrap.
\end{enumerate}

\end{document}
